Pairwise-complete correlation considered dangerous

### 2015-05-26 missing.Rmd
missing

If you really don't want to do that for some reason, consider imputing the missing values. The simplest available replaces missing values in each column with the mean of the non-missing values in the respective column:
```{r}
m = mean(na.omit(x[,3]))
xi = x
xi[is.na(x)] = m
cor(xi)
```

>>>>

If you really don't want to do that for some reason, consider imputing the missing values. The simplest available method replaces missing values in each column with the mean of the non-missing values in the respective column:
```{r}
m = mean(na.omit(x[,3]))
xi = x
xi[is.na(x)] = m
cor(xi)
```
This can be done really efficiently when "centering" a matrix by simply replacing missing values of the centered matrix with zero.
